Distances

### 2020-04-11 03_distances.Rmd
Set up python script to take projected graph

```{python graph}
graph = ox.graph_from_place('New York, New York, USA', network_type='walk')
graph_proj = ox.project_graph(graph)
```

@@

```{r park_points}
park_points <- open_space_points %>%
  st_transform(4326) %>%
  mutate(
    LONGITUDE = st_coordinates(.)[, 1],
    LATITUDE = st_coordinates(.)[,2]
  ) %>%
  st_set_geometry(NULL) %>%
  as_tibble()
```

@@

First, we bring the park points we sampled into a pandas data frame with
the park id as the index.
```{python park_points_py}
park_points = pd.DataFrame(r.park_points)
# TODO: run for all park points
park_ids = park_points.sample(2).id

>>>>

```{python graph}
graph = ox.graph_from_place('New York, New York, USA', network_type='walk')
# project to 18N, EPSG = 32618
graph_proj = ox.project_graph(graph, to_crs="+proj=utm +zone=17 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
graph_simple = nx.DiGraph(graph_proj)
```

@@

```{r park_points}
park_points <- open_space_points %>%
  st_transform(32618) %>%
  mutate(
    LONGITUDE = st_coordinates(.)[, 1],
    LATITUDE = st_coordinates(.)[,2]
  ) %>%
  st_set_geometry(NULL) %>%
  as_tibble()

write_csv(park_points, "data/park_points_nonode.csv")
```

@@

First, we bring the park points we sampled into a pandas data frame with
the park id as the index.
```{python park_points_py}
park_points = pd.DataFrame(r.park_points)
# TODO: run for all park points
park_ids = park_points.sample(5).id
